\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                              %
% Tyler Bendele                                                %
% ECE351 and Section 51                                        %
% Lab 0                                                        %
% Due Date: January 25, 2022                                   %
% Introductory Lab for installing software and testing it      %
%                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Lab 0: Setting Up the Environment}
\author{Tyler Bendele}

\begin{document}
\maketitle


\section{Summary}

Lab 0 starts by first going over the different software that we will end up using this semester. The list of software included Python 3.x, Spyder, Anaconda prompt, and several useful packages. The lab then provides instructions on how to download and install the software. I then verify that the installation of Spyder was successful by opening it and running code that imported the packages: numpy, matplotlib, and scipy. After that works, the lab has me install the control package using the Anaconda prompt window and then test the Spyder code to see if that works too. The final part of the lab has me create a GitHub account. In this account I create two repositories. One repository is used for Python code and the other is used for Latex code.

\section{Questions}
\begin{enumerate}
\item What did you do over last summer, or what are you planning to do this upcoming summer?
\newline
Last summer, I worked most of it at a fast food restaurant to make money for this year. This upcoming summer, I am hoping to get an internship to get experience and make money.

\item What do you personally want to get out of this lab?
\newline
Personally, I would like to learn as many new things as I can in this lab. 
\end{enumerate}


\end{document}